### 2025-07-14 player-evaluation.qmd
20250713 - Bohr quote
20250714 - volume

@@

It is also important to consider a player's opportunity and usage, which are influenced by many factors, including the skill of the player, the skill of their teammates, the role of the player on the team, the coaching style, the strategy of the opposing team, game scripts, etc.
In terms of the player's opportunity and usage, how many snaps do they get?
How many routes do they run?
How many touches and/or targets do they receive?
Being on the field for more snaps, running more routes, and receiving more touches and/or targets means that the player has more opportunities to score fantasy points.
Are they targeted in the red zone?
Red zone targets are more likely to lead to touchdown scoring opportunities, which are particularly valuable in fantasy football.

>>>>

> "*It is very difficult to predict—especially the future.*"
>
> --- Neils Bohr

@@

It is also important to consider a player's opportunity, usage, and volume, which are influenced by many factors, including the skill of the player, the skill of their teammates, the role of the player on the team, the coaching style, the strategy of the opposing team, game scripts, etc.
In terms of the player's opportunity and usage, how many snaps do they get?
How many routes do they run?
How many touches and/or targets do they receive?
Being on the field for more snaps, running more routes, and receiving more touches and/or targets means that the player has more opportunities to score fantasy points.
What is the depth of their targets?
Are they receiving short passes or long passes?
Players who receive longer passes may have an opportunity for more fantasy points but also may be more volatile (i.e., less [consistent](#sec-evalHistoricalConsistency)).
Are they targeted in the red zone?
Red zone targets are more likely to lead to touchdown scoring opportunities, which are particularly valuable in fantasy football.
